---
title: "p8105_hw1_rc3520"
author: "Ruyi Chen"
date: "2023-09-23"
output: html_document
---
```{r}
library (tidyverse)
```

#Problem 1

```{r}
library(moderndive)
data("early_january_weather")
```

## Description of the early_january_weather data set

1.  This data set has `r nrow(early_january_weather)` rows, and `r ncol(early_january_weather)` columns. 
2.  Origin represents weather station; Year, month, day and hour represent time of recording;temp and dewp represent temperature and dewpoint in F; humid represents relative humidity; wind_dir, wind_speed and wind_gust represent wind direction (in degrees), speed and gust speed (in mph); precip represents precipitation, in inches; pressure represents sea level pressure in millibars; visib represents visibility in miles; time_hour represents date and hour of the recording as a POSIXct date.
3.  The mean temperature is `r mean(pull(early_january_weather, temp), na.rm = TRUE)`.

##Make a scatterplot of temp (y) vs time_hour (x)
```{r Make a scatterplot of temp (y) vs time_hour (x)}
ggplot(early_january_weather, aes(x = hour, y = temp, color=humid)) + 
  geom_point() + 
  ggtitle('Scatterplot of temp (y)  vs time_hour (x)') +
  xlab('time_hour ') + ylab('temp(F)')
```

## Export the scatterplot to project directory
```{r export scatterplot to project directory}
ggsave("Scatterplot of temp vs time_hour.pdf")
```